### 2013-06-05 inst/examples/BUGS/process-noise-only.Rmd

```{r allen-mcmc-local, dependson=c("allen-model-local", "allen-pars", "jags-setup"), results="hide"}
jags.params=c("K","logr0","logtheta","stdQ") # be sensible about the order here
jags.inits <- function(){
  list("K"= 8 * rlnorm(1,0, 0.1),
       "logr0"=log(2 * rlnorm(1,0, 0.5) ),
       "logtheta"=log(  5 * rlnorm(1,0, 0.1) ), 
       "stdQ"= abs( 0.2 * rlnorm(1,0, 0.1)),
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}

set.seed(1234)
# parallel refuses to take variables as arguments (e.g. n.iter = 1e5 works, but n.iter = n doesn't)
allen_jags <- do.call(jags, list(data=jags.data, inits=jags.inits, 
                                      jags.params, n.chains=n.chains, 
                                      n.iter=n.iter, n.thin=n.thin, 
                                      n.burnin=n.burnin, 
                                      model.file="allen_process.bugs"))

@@

```{r myers-mcmc-local, dependson="myers-model-local"}
jags.params=c("logr0", "logtheta", "logK", "stdQ")
jags.inits <- function(){
  list("logr0"=log(rlnorm(1,0,.1)), 
       "logK"=log(10 * rlnorm(1,0,.1)),
       "logtheta" = log(2 * rlnorm(1,0,.1)),  
       "stdQ"=sqrt(0.5) * rlnorm(1,0,.1),
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}
set.seed(12345)
myers_jags <- do.call(jags, 
                      list(data=jags.data, inits=jags.inits, jags.params, 
                           n.chains=n.chains, n.iter=n.iter, n.thin=n.thin,
                           n.burnin=n.burnin, model.file="myers_process.bugs"))
recompile(myers_jags)
myers_jags <- do.call(autojags, 
                      list(myers_jags, n.update=n.update, n.iter=n.iter, 
                           n.thin = n.thin, progress.bar="none"))
```

>>>>

```{r allen-mcmc-local, dependson=c("allen-model-local", "allen-pars", "jags-setup"), results="hide"}
jags.params=c("K","logr0","logtheta","stdQ") # be sensible about the order here
jags.inits <- function(){
  list("K"= 8 * rlnorm(1,0, 0.1),
       "logr0"=log(2 * rlnorm(1,0, 0.1) ),
       "logtheta"=log(  5 * rlnorm(1,0, 0.1) ), 
       "stdQ"= abs( 0.1 * rlnorm(1,0, 0.1)),
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}

set.seed(1234)
# parallel refuses to take variables as arguments (e.g. n.iter = 1e5 works, but n.iter = n doesn't)
allen_jags <- do.call(jags.parallel, list(data=jags.data, inits=jags.inits, 
                                      jags.params, n.chains=n.chains, 
                                      n.iter=n.iter, n.thin=n.thin, 
                                      n.burnin=n.burnin, 
                                      model.file="allen_process.bugs"))

@@

```{r myers-mcmc-local, dependson="myers-model-local"}
jags.params=c("logr0", "logtheta", "logK", "stdQ")
jags.inits <- function(){
  list("logr0"=log(rlnorm(1,0,.1)), 
       "logK"=log(10 * rlnorm(1,0,.1)),
       "logtheta" = log(2 * rlnorm(1,0,.1)),  
       "stdQ"=sqrt(0.5) * rlnorm(1,0,.1),
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}
set.seed(12345)
myers_jags <- do.call(jags.parallel, 
                      list(data=jags.data, inits=jags.inits, jags.params, 
                           n.chains=n.chains, n.iter=n.iter, n.thin=n.thin,
                           n.burnin=n.burnin, model.file="myers_process.bugs"))
recompile(myers_jags)
myers_jags <- do.call(autojags, 
                      list(myers_jags, n.update=n.update, n.iter=n.iter, 
                           n.thin = n.thin, progress.bar="none"))
```
